\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[tmargin=1cm, bmargin=1cm, lmargin=2cm, rmargin=2cm]{geometry}
\usepackage{array}
\usepackage{enumitem}

% Predefined colors
\usepackage{xcolor}
\definecolor{bgleftcol}{HTML}{01303f}
\definecolor{headercolor}{HTML}{02577a}
\definecolor{iconcolor}{HTML}{02577a}
\definecolor{lightbg}{HTML}{f8f9fa}

% URL
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=headercolor,
    urlcolor=headercolor,
    citecolor=headercolor
}

% Do not indent paragraphs
\setlength{\parindent}{0pt}

% Section and subsection styles
\usepackage{titlesec}
\titleformat{\section}%
    {\normalfont\huge\bfseries\color{headercolor}}%
    {\thesection}{1em}{}%
    [\color{headercolor}{\titlerule[0.8pt]}\vspace{0.3cm}]

\titleformat{\subsection}%
    {\normalfont\Large\bfseries\color{headercolor}}%
    {\thesubsection}{1em}{}%
    [\color{headercolor}{\titlerule[0.5pt]}\vspace{0.2cm}]

\titleformat{\subsubsection}%
    {\normalfont\large\bfseries\color{headercolor}}%
    {\thesubsubsection}{1em}{}%

% Job entry
\newcommand{\jobentry}[3]{
    {\Large\bfseries #1}
    %
    \hfill
    %
    #2
    %
    \vspace{0.2cm} \\
}

\newcommand{\projectentry}[2]{
    {\large\bfseries #1 \hfill #2} \\ \vspace{-0.5cm}
}

% Skill entry for inline skills
\newcommand{\skillentry}[2]{
    {\large\color{iconcolor}#1} #2 \quad
}

% Contact info command
\newcommand{\contactinfo}[2]{
    {\large\color{iconcolor}#1} #2 \quad
}

% Icons
\usepackage[fixed]{fontawesome5}

% Sensitive information
\input{private/private-information.tex}
\def\myname{Juan Sebastián Cárdenas-Rodríguez}

\pagestyle{empty}
\begin{document}

% Header section
\begin{center}
    {\Huge\bfseries\color{headercolor}\myname}

    \vspace{0.3cm}

    {\Large Senior Full Stack Developer}

    \vspace{0.5cm}

    % Contact information in a single line
    \contactinfo{\faPhone}{\myphone}
    \contactinfo{\faAt}{\myemail}
    \contactinfo{\faGithub}{\href{https://github.com/juanscr}{juanscr}}
    {\large\color{iconcolor}\faHome} \myhome
\end{center}

% Professional summary
\colorbox{lightbg}{\parbox{\dimexpr\textwidth-2\fboxsep\relax}{
\vspace{0.3cm}
I am a senior engineer with over four years of experience in software
development, serving in roles such as tech lead and full-stack developer.
Throughout my career, I've been head of projects focusing on improving the
human experience through technology. Whether improving efficiency, enhancing
connectivity, or delivering valuable products, I prioritize executing
high-quality engineering projects that make a tangible difference. I take pride
in leading teams to construct maintainable software using cutting-edge
technologies and best coding practices.
\vspace{0.3cm}
}}

\section*{Recent Experience}

\jobentry{Software Engineer II at Microsoft}{July, 2024 -- Today}

\begin{tabular}{l m{15.7cm}}
    {\large\color{iconcolor}\faReact} & Became an informal leader in React
    frontend development, solving complex issues like memory leaks and infinite
    rendering scenarios. \\[0.5cm]

    {\large\color{iconcolor}\faServer} & Maintained and developed SDKs for Web
    and Mobile platforms using \texttt{typescript} and \texttt{kotlin},
    enabling application hosting across multiple environments. \\[0.5cm]

    {\large\color{iconcolor}\faRobot} & Collaborated with BizChat (Copilot)
    team by supporting left rail frontend development and maintaining MetaOS
    code features for AI chat integration.\\[0.5cm]

    {\large\color{iconcolor}\faTools} & Led technical solutions for critical
    frontend challenges, establishing best practices and mentoring team members
    on React optimization techniques.
\end{tabular}

\vspace{0.5cm}

\jobentry{Head of Software Development at LCH}{2021 -- 2024}

In the 90s, Laboratorio Clínico Hematológico developed an in-house COBOL system
to handle the information flow in the laboratory and needed a technical
migration to a more up to date stack.

\vspace{0.3cm}

\begin{tabular}{l m{15.7cm}}
    {\large\color{iconcolor}\faServer} & Created and maintained a microservice
    architecture in self hosted infrastructure with containerization technology
    (\texttt{docker}), load balancers (\texttt{nginx}) and virtual machines
    with \texttt{linux}. \\[0.5cm]

    {\large\color{iconcolor}\faHome} & Constructed a team from the ground up
    and lead them to create high quality products using agile methodologies.
    \\[0.5cm]

    {\large\color{iconcolor}\faFlask} & Created full stack software using
    \texttt{python}, \texttt{rust} and \texttt{typescript} using frameworks
    such as \texttt{vue}, \texttt{react}, \texttt{flask}, \texttt{axum} and
    \texttt{nuxtjs}.
\end{tabular}

\vspace{0.5cm}

\jobentry{Founding Engineer at Ember AI}{April, 2024 - July, 2024}

Ember AI transforms the world of cryptocurrency by making it as simple as
texting a friend.

\vspace{0.3cm}

\begin{tabular}{l m{15.7cm}}
    {\large\color{iconcolor}\faServer} & Established a reliable continuous
    integration and delivery pipeline using \texttt{Docker}, Github Actions and
    \texttt{Linux}, ensuring rapid and reliable product deployment. \\[0.5cm]

    {\large\color{iconcolor}\faBuilding} & Created type-safe and reliable
    event-driven APIs using \texttt{typescript} and \texttt{python}, along with
    frontends in \texttt{react} that interacted with smart contracts. \\[0.5cm]

    {\large\color{iconcolor}\faRobot} & Developed backend services integrating
    LLM models for multi-agent communication systems, enabling intelligent
    resolution of user DeFi needs through automated agent coordination.
\end{tabular}

\begin{flushright}
%
    \small Full work history available at
    \href{https://www.linkedin.com/in/juanscr-fullstack}{\faLinkedin juanscr-fullstack}
    %
    \end{flushright}

\vfill
\subsection*{Key Projects}

\projectentry{Cauterization Child Proxying Communication}{Microsoft}

\begin{itemize}
    \item Executed a critical security initiative to remove Teams JS proxying
    mechanisms, requiring deep understanding of communication modules and
    refactoring core security components for hosted apps in various hosts.

    \item Reduced child proxying messages by 50\% and created a more secure app
    ecosystem by eliminating vulnerable patterns. Enhanced authentication
    systems that previously relied on the deprecated proxying pattern.

    \item Coordinated cross-functional collaboration with project managers for
    app migration, partnered with partner teams for deprecating this pattern,
    and aligned with senior team members to establish unified security vision.
\end{itemize}

\projectentry{DeFi Graph Action Database}{Ember AI}

\begin{itemize}
    \item Designed and refactored an in-memory graph database for mapping all
    possible DeFi actions and token transformations, enabling conversion of user
    intent into executable on-chain actions. This graph structure provided a
    generalized layer for routing actions across different DeFi protocols.

    \item Created easy-to-use MCP tools for AI coordination, achieving sub-15ms
    latency for user requests through optimized graph queries and efficient
    action resolution algorithms.

    \item Added plugin interface for seamless open source contributions,
    allowing new actions to be integrated into the graph. Optimized data
    initialization using multicall contracts to batch data retrieval and storage
    operations.
\end{itemize}

\projectentry{CobolQL}{LCH}

\begin{itemize}
    \item Designed and maintained CobolQL, a GraphQL API that exposed
        proprietary, poorly normalized data from a monolithic Cobol app,
        enabling external integrations, frontend upgrades, and clearer data
        access. CobolQL became a central piece of the microservices
        architecture, abstracting data access into a scalable, unified endpoint.

    \item Solved the core data access bottleneck, unlocking faster development
        across teams. As such, this API enabled the creation of over 5 Vue apps
        within 6 months, accelerating frontend delivery and reducing legacy
        constraints.

    \item Overcame significant performance limitations by optimizing GraphQL
        resolution. This was done by batching Cobol data responses into single
        API calls, reducing overhead and avoiding saturation of the legacy
        system.
\end{itemize}

\section*{Technical Skills}
%
\begin{tabular}{l m{13.2cm}}
%
{\large\color{iconcolor}\faJs} \textbf{TypeScript} & Frontend (React, Vue) and
backend (Express, Next.js, Nuxt.js) development \\[0.2cm]
%
{\large\color{iconcolor}\faRust} \textbf{Rust} & CLI automation and
high-performance backend development with Axum \\[0.2cm]
%
{\large\color{iconcolor}\faPython} \textbf{Python} & Data analysis and API
development using FastAPI and Flask \\[0.2cm]
%
{\large\color{iconcolor}\faLinux} \textbf{DevOps} & Linux server management and
app containerization using Docker. Automation pipelines with GitHub Actions and
Bitbucket pipelines
%
\end{tabular}

\section*{Education}

Mathematical Engineer, Universidad EAFIT. (2017 - 2021)

\end{document}